Slitasje og kjørespor

### 2023-01-27 DRAFT_slitasjeOgKjørespor.Rmd
doc: Way forward

@@

Bootstrapping of nin-polygons per infrastructure class and region?

>>>>

Alternatively I can rasterize the indicator map, and mask it using a perfectly aligned ET map. This might be faster.

### Crop to ET
This is a very heavy operation.
```{r, eval=F}
mireET <- sf::st_read("R:/Kladd/Myr/Myrmodell.gdb")
```

```{r, eval=F}
wetlands_slitasje_extr_cropped <- sf::st_intersection(wetlands_slitasje_extr, mireET)
```

### Aggregate to region

```{r, eval=F}
wetlands_slitasje_extr_cropped_reg <- ea_spread(indicator_data = wetlands_slitasje_extr_cropped,
                                      indicator = i_2020,
                                      regions = regions,
                                      groups = ?)
```

@@

The calculations of indicator uncertainty is done with bootstrapping, as is described in eaTools.
